---
title: "GLUE-urbanQuant"
subtitle: "Q1: City-Specific Regressions"
author: "David Murray-Stoker"
output:
  pdf_document:
    toc: true
    toc_depth: 4
    fig_caption: yes
    latex_engine: xelatex
always_allow_html: true
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(results = "hold", fig.pos = "H", fig.align = "center", out.width = "92.5%")
options(knitr.graphics.error = FALSE)
kableExtra::usepackage_latex("float")
```

```{r Load Packages for R Markdown, include = FALSE}
library(kableExtra)
library(knitr)
```

```{r Load Packages & Data, include = FALSE}
## Load the tidyverse
library(tidyverse)

## Packages for analyses
library(broom)
library(car)
library(easystats)
library(emmeans)
```




\newpage
# Load Data

```{r Load Data, echo = TRUE}
## Load data
urban.quantification.full.data <- read_csv(
  file = "data/analysis_data/urbanQuant-full_data.csv",
  col_types = c("fffnnninnnnnnininnnnnnn"),
  show_col_types = FALSE
)

## Split the data into a list; one dataframe per city
city.specific.data.list <- urban.quantification.full.data %>%
  group_split(City) %>%
  setNames(unique(urban.quantification.full.data$City))
```




\newpage
# City-Specific Regressions


## Set Functions

```{r fit_environmental_variable_by_distance_model Function, echo = TRUE}
# Fit a linear model with an environmental variable as the response and distance,
# sampling design, and the two-way interaction as predictors.

## Set the function
fit_environmental_variable_by_distance_model <- function(df, response_variable) {
  # Set the response variable
  Response_Variable <- df %>% pull(response_variable)

  ## Fit the linear mixed-effects model
  fitted.regression <- lm(
    Response_Variable ~ Standardized_Distance + Sampling_Design + Standardized_Distance:Sampling_Design,
    data = df
  )

  return(fitted.regression)
}
```

\vspace{10pt}

```{r environmental_variable_by_distance_model_ANOVA Function, echo = TRUE}
# Extract and format the ANOVA table for a fitted environmental
# variable-by-distance model

## Set the function
environmental_variable_by_distance_model_ANOVA <- function(fitted_model) {
  # ANOVA with Type III sums-of-squares
  regression.anova.table <- Anova(
    mod = fitted_model,
    type = "III"
  )

  # Format the ANOVA table for later data summaries
  formatted.regression.anova.table <- regression.anova.table %>%
    rownames_to_column(var = "Term") %>%
    select("Term", "Pr(>F)") %>%
    slice(2:4) %>%
    pivot_wider(names_from = "Term", values_from = "Pr(>F)") %>%
    rename(
      Distance = Standardized_Distance,
      Distance_by_Sampling_Design = `Standardized_Distance:Sampling_Design`
    ) %>%
    mutate_at(1:3, round, 5)

  return(formatted.regression.anova.table)
}
```


\newpage
```{r environmental_variable_by_distance_model_effect_sizes Function, echo = TRUE}
# Calculate effect sizes for a fitted environmental variable-by-distance model

## Set the function
environmental_variable_by_distance_model_effect_sizes <- function(fitted_model) {
  # Get the adjusted R-squared
  regression.R.squared <- summary(fitted_model)$adj.r.squared

  # Effect sizes for the fixed effects
  regression.eta.squared <- eta_squared(fitted_model, partial = TRUE, ci = 0.95)

  # Combine the effect sizes into a summary table
  regression.effect.size.summary.table <- tibble(
    R2_adjusted = regression.R.squared,
    eta2_Predictor = regression.eta.squared[1, 2],
    eta2_Sampling_Design = regression.eta.squared[2, 2],
    eta2_Interaction = regression.eta.squared[3, 2]
  )

  return(regression.effect.size.summary.table)
}
```

\vspace{10pt}

```{r deviation_regression_predictions Function, echo = TRUE}
# Extract and format predictions (i.e., slopes) for a fitted environmental
# variable-by-distance model.

## Set the function
environmental_variable_by_distance_model_predictions <- function(fitted_model) {
  # Get the predictions from the fitted regression
  regression.predictions <- emtrends(
    fitted_model,
    specs = pairwise ~ Sampling_Design,
    var = "Standardized_Distance",
    weights = "cells",
    adjust = "none"
  )

  # Format the model predictions for later data summaries and figures
  formatted.regression.predictions <- regression.predictions$emtrends %>%
    as_tibble() %>%
    rename(Estimated_Slope = Standardized_Distance.trend) %>%
    select(Sampling_Design:SE)


  return(formatted.regression.predictions)
}
```


\newpage
## ISC

```{r ISC Regressions & Results, echo = TRUE}
## Fit the regressions
ISC.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "ISC_Mean"
)

## ANOVA
ISC.regression.ANOVAs <- map_dfr(
  ISC.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
ISC.regression.effect.sizes <- map_dfr(
  ISC.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
ISC.regression.predictions <- map_dfr(
  ISC.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## HII

```{r HII Regressions & Results, echo = TRUE}
## Fit the regressions
HII.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "HII"
)

## ANOVA
HII.regression.ANOVAs <- map_dfr(
  HII.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
HII.regression.effect.sizes <- map_dfr(
  HII.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
HII.regression.predictions <- map_dfr(
  HII.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## Mean NDVI

```{r Mean NDVI Regressions & Results, echo = TRUE}
## Fit the regressions
mean.NDVI.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "Mean_NDVI"
)

## ANOVA
mean.NDVI.regression.ANOVAs <- map_dfr(
  mean.NDVI.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
mean.NDVI.regression.effect.sizes <- map_dfr(
  mean.NDVI.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
mean.NDVI.regression.predictions <- map_dfr(
  mean.NDVI.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## Min NDVI

```{r Min NDVI Regressions & Results, echo = TRUE, eval = FALSE}
## Fit the regressions
min.NDVI.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "Min_NDVI"
)

## ANOVA
min.NDVI.regression.ANOVAs <- map_dfr(
  min.NDVI.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
min.NDVI.regression.effect.sizes <- map_dfr(
  min.NDVI.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
min.NDVI.regression.predictions <- map_dfr(
  min.NDVI.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## Max NDVI

```{r Max NDVI Regressions & Results, echo = TRUE, eval = FALSE}
## Fit the regressions
max.NDVI.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "Max_NDVI"
)

## ANOVA
max.NDVI.regression.ANOVAs <- map_dfr(
  max.NDVI.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
max.NDVI.regression.effect.sizes <- map_dfr(
  max.NDVI.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
max.NDVI.regression.predictions <- map_dfr(
  max.NDVI.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## Mean Annual Temperature

```{r Mean Annual Temperature Regressions & Results, echo = TRUE}
## Fit the regressions
mean.annual.temperature.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "Mean_Annual_Temperature"
)

## ANOVA
mean.annual.temperature.regression.ANOVAs <- map_dfr(
  mean.annual.temperature.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
mean.annual.temperature.regression.effect.sizes <- map_dfr(
  mean.annual.temperature.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
mean.annual.temperature.regression.predictions <- map_dfr(
  mean.annual.temperature.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## Temperature Seasonality

```{r Temperature Seasonality Regressions & Results, echo = TRUE}
## Fit the regressions
temperature.seasonality.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "Temperature_Seasonality"
)

## ANOVA
temperature.seasonality.regression.ANOVAs <- map_dfr(
  temperature.seasonality.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
temperature.seasonality.regression.effect.sizes <- map_dfr(
  temperature.seasonality.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
temperature.seasonality.regression.predictions <- map_dfr(
  temperature.seasonality.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## Range Annual Temperature

```{r Range Annual Temperature Regressions & Results, echo = TRUE}
## Fit the regressions
range.annual.temperature.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "Range_Annual_Temperature"
)

## ANOVA
range.annual.temperature.regression.ANOVAs <- map_dfr(
  range.annual.temperature.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
range.annual.temperature.regression.effect.sizes <- map_dfr(
  range.annual.temperature.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
range.annual.temperature.regression.predictions <- map_dfr(
  range.annual.temperature.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## Annual Precipitation

```{r Annual Precipitation Regressions & Results, echo = TRUE}
## Fit the regressions
annual.precipitation.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "Annual_Precipitation"
)

## ANOVA
annual.precipitation.regression.ANOVAs <- map_dfr(
  annual.precipitation.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
annual.precipitation.regression.effect.sizes <- map_dfr(
  annual.precipitation.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
annual.precipitation.regression.predictions <- map_dfr(
  annual.precipitation.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## Precipitation Seasonality

```{r Precipitation Seasonality Regressions & Results, echo = TRUE}
## Fit the regressions
precipitation.seasonality.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "Precipitation_Seasonality"
)

## ANOVA
precipitation.seasonality.regression.ANOVAs <- map_dfr(
  precipitation.seasonality.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
precipitation.seasonality.regression.effect.sizes <- map_dfr(
  precipitation.seasonality.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
precipitation.seasonality.regression.predictions <- map_dfr(
  precipitation.seasonality.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## Aridity Index

```{r Aridity Index Regressions & Results, echo = TRUE}
## Fit the regressions
aridity.index.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "Aridity_Index"
)

## ANOVA
aridity.index.regression.ANOVAs <- map_dfr(
  aridity.index.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
aridity.index.regression.effect.sizes <- map_dfr(
  aridity.index.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
aridity.index.regression.predictions <- map_dfr(
  aridity.index.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(
    City = c(
      rep(names(city.specific.data.list[1:135]), each = 4), rep(names(city.specific.data.list[136]), each = 3)
    )
  )
```


\newpage
## GDP 2005

```{r GDP 2005 Regressions & Results, echo = TRUE}
## Fit the regressions
GDP.2005.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "GDP_2005"
)

## ANOVA
GDP.2005.regression.ANOVAs <- map_dfr(
  GDP.2005.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
GDP.2005.regression.effect.sizes <- map_dfr(
  GDP.2005.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
GDP.2005.regression.predictions <- map_dfr(
  GDP.2005.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## SSP1 2030

```{r SSP1 2030 Regressions & Results, echo = TRUE}
## Fit the regressions
SSP1.2030.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "SSP_1_2030"
)

## ANOVA
SSP1.2030.regression.ANOVAs <- map_dfr(
  SSP1.2030.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
SSP1.2030.regression.effect.sizes <- map_dfr(
  SSP1.2030.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
SSP1.2030.regression.predictions <- map_dfr(
  SSP1.2030.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## SSP1 2100

```{r SSP1 2100 Regressions & Results, echo = TRUE}
## Fit the regressions
SSP1.2100.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "SSP_1_2100"
)

## ANOVA
SSP1.2100.regression.ANOVAs <- map_dfr(
  SSP1.2100.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
SSP1.2100.regression.effect.sizes <- map_dfr(
  SSP1.2100.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
SSP1.2100.regression.predictions <- map_dfr(
  SSP1.2100.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## SSP2 2030

```{r SSP2 2030 Regressions & Results, echo = TRUE}
## Fit the regressions
SSP2.2030.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "SSP_2_2030"
)

## ANOVA
SSP2.2030.regression.ANOVAs <- map_dfr(
  SSP2.2030.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
SSP2.2030.regression.effect.sizes <- map_dfr(
  SSP2.2030.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
SSP2.2030.regression.predictions <- map_dfr(
  SSP2.2030.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## SSP2 2100

```{r SSP2 2100 Regressions & Results, echo = TRUE}
## Fit the regressions
SSP2.2100.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "SSP_2_2100"
)

## ANOVA
SSP2.2100.regression.ANOVAs <- map_dfr(
  SSP2.2100.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
SSP2.2100.regression.effect.sizes <- map_dfr(
  SSP2.2100.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
SSP2.2100.regression.predictions <- map_dfr(
  SSP2.2100.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## SSP5 2030

```{r SSP5 2030 Regressions & Results, echo = TRUE}
## Fit the regressions
SSP5.2030.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "SSP_5_2030"
)

## ANOVA
SSP5.2030.regression.ANOVAs <- map_dfr(
  SSP5.2030.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
SSP5.2030.regression.effect.sizes <- map_dfr(
  SSP5.2030.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
SSP5.2030.regression.predictions <- map_dfr(
  SSP5.2030.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```


\newpage
## SSP5 2100

```{r SSP5 2100 Regressions & Results, echo = TRUE}
## Fit the regressions
SSP5.2100.regression.list <- map(
  city.specific.data.list,
  fit_environmental_variable_by_distance_model,
  response_variable = "SSP_5_2100"
)

## ANOVA
SSP5.2100.regression.ANOVAs <- map_dfr(
  SSP5.2100.regression.list,
  environmental_variable_by_distance_model_ANOVA
) %>%
  add_column(City = names(city.specific.data.list))

## Effect sizes
SSP5.2100.regression.effect.sizes <- map_dfr(
  SSP5.2100.regression.list,
  environmental_variable_by_distance_model_effect_sizes
) %>%
  add_column(City = names(city.specific.data.list))

## Predictions
SSP5.2100.regression.predictions <- map_dfr(
  SSP5.2100.regression.list,
  environmental_variable_by_distance_model_predictions
) %>%
  add_column(City = rep(names(city.specific.data.list), each = 4))
```




\newpage
# Summaries

## Data Management

```{r Results Summary: Data Management, echo = TRUE}
## Combine all ANOVA tables
combined.ANOVA.table <- bind_rows(
  ISC.regression.ANOVAs, HII.regression.ANOVAs, mean.NDVI.regression.ANOVAs,
  mean.annual.temperature.regression.ANOVAs, temperature.seasonality.regression.ANOVAs,
  range.annual.temperature.regression.ANOVAs, annual.precipitation.regression.ANOVAs,
  precipitation.seasonality.regression.ANOVAs, aridity.index.regression.ANOVAs,
  GDP.2005.regression.ANOVAs, SSP1.2030.regression.ANOVAs,
  SSP1.2100.regression.ANOVAs, SSP2.2030.regression.ANOVAs,
  SSP2.2100.regression.ANOVAs, SSP5.2030.regression.ANOVAs,
  SSP5.2100.regression.ANOVAs
) %>%
  add_column(
    urban_environmental_variable = rep(
      c(
        "ISC", "HII", "Mean_NDVI", "Mean_Annual_Temperature",
        "Temperature_Seasonality", "Range_Annual_Temperature",
        "Annual_Precipitation", "Precipitation_Seasonality",
        "Aridity_Index", "GDP_2005", "SSP_1_2030", "SSP_1_2100",
        "SSP_2_2030", "SSP_2_2100", "SSP_5_2030", "SSP_5_2100"
      ),
      each = 136
    )
  )

## Combine all effect size tables
combined.effect.size.table <- bind_rows(
  ISC.regression.effect.sizes, HII.regression.effect.sizes, mean.NDVI.regression.effect.sizes,
  mean.annual.temperature.regression.effect.sizes, temperature.seasonality.regression.effect.sizes,
  range.annual.temperature.regression.effect.sizes, annual.precipitation.regression.effect.sizes,
  precipitation.seasonality.regression.effect.sizes, aridity.index.regression.effect.sizes,
  GDP.2005.regression.effect.sizes, SSP1.2030.regression.effect.sizes,
  SSP1.2100.regression.effect.sizes, SSP2.2030.regression.effect.sizes,
  SSP2.2100.regression.effect.sizes, SSP5.2030.regression.effect.sizes,
  SSP5.2100.regression.effect.sizes
) %>%
  add_column(
    urban_environmental_variable = rep(
      c(
        "ISC", "HII", "Mean_NDVI", "Mean_Annual_Temperature",
        "Temperature_Seasonality", "Range_Annual_Temperature",
        "Annual_Precipitation", "Precipitation_Seasonality",
        "Aridity_Index", "GDP_2005", "SSP_1_2030", "SSP_1_2100",
        "SSP_2_2030", "SSP_2_2100", "SSP_5_2030", "SSP_5_2100"
      ),
      each = 136
    )
  )

## Combine ANOVA and effect size tables
full.regression.results <- combined.ANOVA.table %>%
  full_join(combined.effect.size.table, by = c("City", "urban_environmental_variable")) %>%
  select(
    City, urban_environmental_variable, Distance:Distance_by_Sampling_Design,
    eta2_Predictor:eta2_Interaction, R2_adjusted
  )
```


\newpage
## Summary Tables

```{r Summary Table: Distance Term Tally, echo = FALSE}
distance.term.tally <- full.regression.results %>%
  select(urban_environmental_variable, Distance) %>%
  group_by(urban_environmental_variable) %>%
  summarise(
    "P < 0.001" = (sum(Distance < 0.001) / 136) * 100,
    "P < 0.025" = (sum(Distance < 0.025) / 136) * 100,
    "P < 0.050" = (sum(Distance < 0.050) / 136) * 100,
    "P < 0.100" = (sum(Distance < 0.100) / 136) * 100,
    "P < 0.250" = (sum(Distance < 0.250) / 136) * 100
  )

kable(
  distance.term.tally,
  booktabs = TRUE,
  digits = 3,
  caption = "Percent of models with P-values below specific thresholds for the distance term. Total number of models = 136.",
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Summary Table: Sample Type Term Tally, echo = FALSE}
sample.type.tally <- full.regression.results %>%
  select(urban_environmental_variable, Sampling_Design) %>%
  group_by(urban_environmental_variable) %>%
  summarise(
    "P < 0.001" = (sum(Sampling_Design < 0.001) / 136) * 100,
    "P < 0.025" = (sum(Sampling_Design < 0.025) / 136) * 100,
    "P < 0.050" = (sum(Sampling_Design < 0.050) / 136) * 100,
    "P < 0.100" = (sum(Sampling_Design < 0.100) / 136) * 100,
    "P < 0.250" = (sum(Sampling_Design < 0.250) / 136) * 100
  )

kable(
  sample.type.tally,
  booktabs = TRUE,
  digits = 3,
  caption = "Percent of models with P-values below specific thresholds for the sample type term. Total number of models = 136.",
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```

\vspace{10pt}

```{r Summary Table: Interaction Term Tally, echo = FALSE}
interaction.term.tally <- full.regression.results %>%
  select(urban_environmental_variable, Distance_by_Sampling_Design) %>%
  group_by(urban_environmental_variable) %>%
  summarise(
    "P < 0.001" = (sum(Distance_by_Sampling_Design < 0.001) / 136) * 100,
    "P < 0.025" = (sum(Distance_by_Sampling_Design < 0.025) / 136) * 100,
    "P < 0.050" = (sum(Distance_by_Sampling_Design < 0.050) / 136) * 100,
    "P < 0.100" = (sum(Distance_by_Sampling_Design < 0.100) / 136) * 100,
    "P < 0.250" = (sum(Distance_by_Sampling_Design < 0.250) / 136) * 100
  )

kable(
  interaction.term.tally,
  booktabs = TRUE,
  digits = 3,
  caption = "Percent of models with P-values below specific thresholds for the distance-by-sample-type interaction term. Total number of models = 136.",
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped"))
```


\newpage

```{r Summary Table: P-Values, echo = FALSE}
## Calculate summary statistics for the P-values
P.value.summary.table <- full.regression.results %>%
  select(urban_environmental_variable:Distance_by_Sampling_Design) %>%
  group_by(urban_environmental_variable) %>%
  summarise(
    Distance_P_Value_Mean = mean(Distance),
    Sampling_Design_P_Value_Mean = mean(Sampling_Design),
    Interaction_P_Value_Mean = mean(Distance_by_Sampling_Design),
    Distance_P_Value_SE = sd(Distance) / sqrt(136),
    Sampling_Design_P_Value_SE = sd(Sampling_Design) / sqrt(136),
    Interaction_P_Value_SE = sd(Distance_by_Sampling_Design) / sqrt(136),
    Distance_P_Value_Min = min(Distance),
    Sampling_Design_P_Value_Min = min(Sampling_Design),
    Interaction_P_Value_Min = min(Distance_by_Sampling_Design),
    Distance_P_Value_Max = max(Distance),
    Sampling_Design_P_Value_Max = max(Sampling_Design),
    Interaction_P_Value_Max = max(Distance_by_Sampling_Design)
  )

kable(
  P.value.summary.table,
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the P-values for the city-specific regressions for each urbanization metric.",
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
  landscape()
```

\newpage

```{r Summary Table: Effect Sizes, echo = FALSE}
## Calculate summary statistics for the effect sizes
effect.size.summary.table <- full.regression.results %>%
  select(urban_environmental_variable:eta2_Interaction) %>%
  group_by(urban_environmental_variable) %>%
  summarise(
    Distance_Effect_Size_Mean = mean(eta2_Predictor),
    Sampling_Design_Effect_Size_Mean = mean(eta2_Sampling_Design),
    Interaction_Effect_Size_Mean = mean(eta2_Interaction),
    Distance_Effect_Size_SE = sd(eta2_Predictor) / sqrt(136),
    Sampling_Design_Effect_Size_SE = sd(eta2_Sampling_Design) / sqrt(136),
    Interaction_Effect_Size_SE = sd(eta2_Interaction) / sqrt(136),
    Distance_Effect_Size_Min = min(eta2_Predictor),
    Sampling_Design_Effect_Size_Min = min(eta2_Sampling_Design),
    Interaction_Effect_Size_Min = min(eta2_Interaction),
    Distance_Effect_Size_Max = max(eta2_Predictor),
    Sampling_Design_Effect_Size_Max = max(eta2_Sampling_Design),
    Interaction_Effect_Size_Max = max(eta2_Interaction)
  )

kable(
  effect.size.summary.table,
  booktabs = TRUE,
  digits = 3,
  caption = "Summary of the effect sizes (eta-squared) for the city-specific regressions for each urbanization metric.",
) %>%
  kable_styling(latex_options = c("HOLD_position", "striped", "scale_down")) %>%
  landscape()
```




\newpage
# Export the Results

```{r Export Results: ANOVAs & Effect Sizes, echo = TRUE}
## Combined ANOVA and effect size tables
write_csv(
  full.regression.results,
  "data/analysis_data/city_specific_regressions/full_regression_results.csv"
)
```

```{r Save the Workspace, include = FALSE}
## Save the workspace
save.image("data_analysis/3-analyses/3-city_specific_regressions-workspace.RData")
```










\newpage
# Workspace Information

```{r R Packages, echo = FALSE}
df_session_packages <- devtools::session_info()$packages %>%
  as.data.frame(.) %>%
  filter(attached == TRUE) %>%
  dplyr::select(loadedversion, date) %>%
  rownames_to_column()

colnames(df_session_packages) <- c("Package", "Loaded Version", "Date")

kable(
  df_session_packages,
  booktabs = TRUE,
  caption = "Packages required for data management and analyses."
) %>%
  kable_styling(
    full_width = FALSE,
    latex_options = c("HOLD_position", "striped")
  )
```
